Demo arXiv template

### 2022-12-16 paper/paper.qmd
changes after the meeting

```{r fig-toy-example, eval = TRUE, echo = FALSE}
#| fig-align: center
#| fig-cap: "Standardised Precipitation Evapotranspiration Index (SPEI) calculated with two distribution fits in Step 3 described above: generalised logistic (`glogist`) and generalised extreme value (`gev`) distribution, using the `wichita` data from the package `SPEI`."
#| out-height: 30%
#| out-width: 100%
knitr::include_graphics(here::here("figures/toy-example-spei.png"))
```

@@

@@

An overview of the pipeline is given in @fig-pipeline-steps to illustrate the construction from raw data to the final indexes.
The pipeline includes modules for operations in the spatial, temporal, and multivariate aspects of the data as well as modules for comparing and communicating indexes.
Analysts are free to select the modules they need and arrange them in the order they see fit to construct indexes.
While the starting point of the pipeline is raw data, there are steps prior to this that are crucial to the success of an index. 
For example, the defined index needs to be useful for measuring the concept of interest and variables need to be collected from reliable sources with proper quality control.

The notation used in this section will be first introduced before elaborating on each pipeline module. Let $\mathbf{x}(\mathbf{s};\mathbf{t})$ denote the raw data with spatial, temporal, and multivariate aspects: the spatial dimension $\mathbf{s} =  (s_1, s_2, \cdots, s_n)^\prime$ is defined in the 2D space: $\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2$, the temporal dimension $\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime$ is defined in the 1D space: $\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}$. When more than one variable is involved, the multivariate data can also be written as: $\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime$.

@@

dt %>% 
  ggplot() + 
  geom_point(aes(x= x, y = y)) + 
  geom_line(data = all, aes(x = x, y = y)) + 
  ggrepel::geom_label_repel(
    data = label, aes(x = x, y = y, label =label),
    nudge_y = 0.2, nudge_x = 0.1,
    arrow = arrow(length = unit(0.08, "inches")), min.segment.length = 0) +
  scale_x_continuous(breaks = seq(-3, 3, 1)) + 
  xlab("Density") + 
  ylab("Quantile") + 
  theme_bw() + 
  theme(panel.grid.minor = element_blank())
```

@@

# Incorporating new buliding blocks into the pipeline {#sec-incorporating-new-buliding-blocks-into-the-pipeline}

@@

## Constructing Standardised Precipitation Index (SPI)

@@

## Calculating SPEI with raster data

>>>>

```{r fig-toy-example, eval = TRUE, echo = FALSE}
#| fig-align: center
#| fig-cap: "Standardised Precipitation Evapotranspiration Index (SPEI) calculated with two distribution fits in Step 3 described above: generalised logistic (`glogist`) and generalised extreme value (`gev`) distribution, using the `wichita` data from the package `SPEI`."
#| out-height: 30%
#| out-width: 100%
# library(indri)
# library(dplyr)
# library(lubridate)
# library(lmomco)
# library(ggplot2)
# library(tsibble)
# library(SPEI)
# data(wichita)
# 
# dt <- wichita %>% 
#   aggregate(var = prcp, scale = c(6, 12), index = ym, id = id, gran = month) %>%
#   filter(!is.na(.agg)) %>%
#   normalise(dist = list(gev(), loglogistic()), var = .agg) %>%
#   augment(col = .agg)
# 
# dt %>% 
#   ggplot(aes(x = ym, y = .index, color = .dist)) + 
#   geom_line()
knitr::include_graphics(here::here("figures/toy-example-spei.png"))
```

@@

*any index can be broken down into multiple steps and then we can do things with it: swap, change parameter, etc*

@@

An overview of the pipeline is given in @fig-pipeline-steps to illustrate the construction from raw data to the final indexes.
The pipeline includes eight modules for operations in the spatial, temporal, and multivariate aspects of the data as well as modules for comparing and communicating indexes.
Analysts are free to select the modules they need and arrange them in the order they see fit to construct indexes.
While the starting point of the pipeline is raw data, there are steps prior to this that are crucial to the success of an index. 
For example, the defined index needs to be useful for measuring the concept of interest and variables need to be collected from reliable sources with proper quality control.

Before elaborating each of the eight pipeline modules as subsections, the data notation will be first introduced. Let $\mathbf{x}(\mathbf{s};\mathbf{t})$ denote the raw data with spatial, temporal, and multivariate aspects: the spatial dimension $\mathbf{s} =  (s_1, s_2, \cdots, s_n)^\prime$ is defined in the 2D space: $\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2$, the temporal dimension $\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime$ is defined in the 1D space: $\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}$. When more than one variable is involved, the multivariate data can also be written as: $\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime$.

@@

dt %>% 
  ggplot() + 
  geom_point(aes(x= x, y = y)) + 
  geom_line(data = all, aes(x = x, y = y)) + 
  ggrepel::geom_label_repel(
    data = label, aes(x = x, y = y, label =label),
    nudge_y = 0.2, nudge_x = 0.1,
    arrow = arrow(length = unit(0.08, "inches")), min.segment.length = 0) +
  scale_x_continuous(breaks = seq(-3, 3, 1)) + 
  xlab("Normalised Score") + 
  ylab("Probability") + 
  theme_bw() + 
  theme(panel.grid.minor = element_blank())
```

@@

# Incorporating alternative methods into the pipeline components {#sec-incorporating-new-buliding-blocks-into-the-pipeline}

@@

## A drought index example

@@

easier to make comparison
pick a publication, propose a new index that has this benefit but also correlate highly with the big name indexes

## An example on sustainable development indicators

Weighting

## Calculating indexes on raster data

<!-- Raster data is common data format for delivering large satellite spatio-temporal data.  -->

<!-- Issue 1: variables may be collected at different spatial and temporal extent/ scale, different resolutions and granularities.  -->

<!-- cleaning these variables involves spatial and temporal processing.  -->

<!-- Issue 2: what the data the step is operated on?? -->

<!-- When calculating on raster data, it is confusing on what data the operation is on. Is the operation operated per pixel or across regions, is the operation operated across all the time point, across year, across month etc.  -->

<!-- While it may be clear to researchers themselves, but can be confusing for others who read the analysis for the first time.  -->

<!-- The data structure should be made explicit at each operation on the spatio-temporal raster data, in terms of inputs and outputs. -->

<!-- The raster examples  -->

### 2022-12-16 paper/paper.tex
changes after the meeting

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes modules for operations in the spatial, temporal, and
multivariate aspects of the data as well as modules for comparing and
communicating indexes. Analysts are free to select the modules they need
and arrange them in the order they see fit to construct indexes. While
the starting point of the pipeline is raw data, there are steps prior to
this that are crucial to the success of an index. For example, the
defined index needs to be useful for measuring the concept of interest
and variables need to be collected from reliable sources with proper
quality control.

The notation used in this section will be first introduced before
elaborating on each pipeline module. Let
\(\mathbf{x}(\mathbf{s};\mathbf{t})\) denote the raw data with spatial,
temporal, and multivariate aspects: the spatial dimension
\(\mathbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal dimension \(\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). When more than
one variable is involved, the multivariate data can also be written as:
\(\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime\).

@@

\hypertarget{sec-incorporating-new-buliding-blocks-into-the-pipeline}{%
\section{Incorporating new buliding blocks into the
pipeline}\label{sec-incorporating-new-buliding-blocks-into-the-pipeline}}

@@

\hypertarget{constructing-standardised-precipitation-index-spi}{%
\subsection{Constructing Standardised Precipitation Index
(SPI)}\label{constructing-standardised-precipitation-index-spi}}

@@

\hypertarget{calculating-spei-with-raster-data}{%
\subsection{Calculating SPEI with raster
data}\label{calculating-spei-with-raster-data}}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\emph{any index can be broken down into multiple steps and then we can
do things with it: swap, change parameter, etc}

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes eight modules for operations in the spatial, temporal,
and multivariate aspects of the data as well as modules for comparing
and communicating indexes. Analysts are free to select the modules they
need and arrange them in the order they see fit to construct indexes.
While the starting point of the pipeline is raw data, there are steps
prior to this that are crucial to the success of an index. For example,
the defined index needs to be useful for measuring the concept of
interest and variables need to be collected from reliable sources with
proper quality control.

Before elaborating each of the eight pipeline modules as subsections,
the data notation will be first introduced. Let
\(\mathbf{x}(\mathbf{s};\mathbf{t})\) denote the raw data with spatial,
temporal, and multivariate aspects: the spatial dimension
\(\mathbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal dimension \(\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). When more than
one variable is involved, the multivariate data can also be written as:
\(\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime\).

@@

\hypertarget{sec-incorporating-new-buliding-blocks-into-the-pipeline}{%
\section{Incorporating alternative methods into the pipeline
components}\label{sec-incorporating-new-buliding-blocks-into-the-pipeline}}

@@

\hypertarget{a-drought-index-example}{%
\subsection{A drought index example}\label{a-drought-index-example}}

@@

easier to make comparison pick a publication, propose a new index that
has this benefit but also correlate highly with the big name indexes

\hypertarget{an-example-on-sustainable-development-indicators}{%
\subsection{An example on sustainable development
indicators}\label{an-example-on-sustainable-development-indicators}}

Weighting

\hypertarget{calculating-indexes-on-raster-data}{%
\subsection{Calculating indexes on raster
data}\label{calculating-indexes-on-raster-data}}
